Adopting agile in the large: motivations, success factors and challenges

### 2014-04-11 journal/article.tex
Meta-analysis
Journals vs. conferences

The results of this study include findings from 52 primary studies presenting
how 40 different large organizations introduce agile software development.

>>>>

The results of this study include findings from 52 primary studies presenting
how 40 different large organizations introduce agile software development. Most
of the included studies were experience reports (45 studies), and in many cases
it was evident that the author had been personally involved in the transformation.
Only 6 of the included studies had a research method explicitly stated. One of
the studies was an interview article. The publication forums of the primary
studies were distributed so that 57 sources were conference proceedings, 4
sources were journal articles, and one source was a technical report.
